Differential invariant signatures for planar Lie group transformations of images

### 2020-11-17 paper/newpaper.tex
updates'

\begin{document}
\maketitle
\begin{abstract}
Object recognition, planar transformation, invariants, differential invariant signature, demo of 3 methods with examples for planar Lie groups, discussion of utility
\end{abstract}

% REQUIRED
\begin{keywords}
Object recognition, planar transformation, invariants, differential invariant signature
\end{keywords}

@@

\section{Introduction}
\todo[inline]{
Abstract
Literature

Sim(2) by contraction
A(2) by transvectant
Check signatures for Mobius etc.

Discussion
}

@@

In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another. These constraints lead one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology. This is sufficient to compute, e.g., derivatives of an object. For this reason we focus on differential invariants. The disadvantage of such invariants, as we shall discuss, is the need to compute several orders of spatial derivative of the image.

@@

\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}

A variety of function spaces have allowed for the creation of different sets of invariants for particular groups. For the Euclidean group, the Fourier transform provides a useful tool, and this can be extended to the affine group using the Fourier-Mellin transform and the bispectrum. Alternatively, integral invariants and moments can be computed. For the similarity group applied to images the seminal reference is \cite{Hu1962}, but see also~\cite{}. 
\cite{Hickman2011,Abu-Mostafa1984,Kakarala2010,Flusser2009,Papakostas2013}
\cite{Manay2006,Negrinho2013,Ghorbel1994,Turski2006}
\cite{Reddy1996,Gauthier2008,Kakarala2011,Smach2007}

The other group that has been of particular interest for image analysis is the projective group, because of its ubiquity in images from cameras. Summarise these...
\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}

Diff invs and sigs

An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}. The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:MF}) and then the signature set of a maximal set of functionally independent invariants is identified. A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.

This is essential if the
signature is to be used to detect similarity of images, but it fails for the rational
invariants found in the literature.

There has been a long-standing interest in constructing invariants for image recognition. 
\cite{VanGool1995,Wood1996,Zhang2019,Faugeras1994,Gros1992,Taubin1992,Lenz1990,Florack1993}

@@

>>>>

\begin{document}
\maketitle
\begin{abstract}
Camera motion imposes transformations on the objects in an image, and these transformations will differ for objects at different positions relativele to the camera. Typically these transformations will be elements of planar Lie groups. While there have been significant advances in object recognition using machine learning in recent years, the question of how to recognise an object in an image as its appearance varies through camera motion and similar effects remains open. We consider how differential invariant signatures can be derived for each of the transformation groups, and how the underlying invariances reflect the group-subgroup structure of the transformation groups.

There are a variety of methods that can be used to identify differential invariants, and we provide examples of three of them: tensor contraction, transvectants, and the method of moving frames. We use the resulting invariants to construct practical sets to form three-dimensional invariant signatures. These signatures are not necessarily complete: the image cannot always be reconstructed uniquely up to transformation, but they are plottable, and depend at worst on third derivatives, although more channels of information, such as colour images, can reduce the highest order to derivate needed in some cases. We demonstrate the invariant signatures for each transformation group based on a simple smooth image. A full consideration of how these signatures could be used in practice will require effective methods to numerically approximate derivatives effectively for images.
\end{abstract}

% REQUIRED
\begin{keywords}
Object recognition, planar transformation, planar Lie groups, invariants, differential invariant signature
\end{keywords}

@@

\section{Introduction}
\todo[inline]{
Literature
Discussion -- syzygies

Sim(2) by contraction
A(2) by transvectant
Check signatures for Mobius etc.
}

@@

In order for the invariant signatures to be useful to identify similarity in images, there are two key considerations: they must vary continuously with respect to the image, either for all smooth images or for all except a set of sufficiently high codimension, and they must be robust with respect to occlusions, where one object obscures some part of another. Thse constraints are essential if the signature is to be used to detect similarity of images, but the first fails for the rational invariants found in the literature. Such considerations lead one naturally to consider local invariants, i.e., those defined using each point of the object as its own basepoint, together with a neighbourhood in some topology. This is sufficient to compute, e.g., derivatives of an object. For this reason we focus on differential invariants. The disadvantage of such invariants, as we shall discuss, is the need to compute several orders of spatial derivative of the image.

@@

@@

\cite{Cayley,Littlewood44,Cartan52,Patterson1928,Veblen1872,Lie1884}
\cite{VanGool1995}

\kakarala2011

There has been a long-standing interest in constructing invariants for image recognition.
Wood1996,
Taubin1992
A variety of function spaces have allowed for the creation of different sets of invariants for particular groups. For the Euclidean group, the Fourier transform provides a useful tool~\cite{Ghorbel1994,Turski2006,Smach2007,Gauthier2008}, and this can be extended to the affine group using the Fourier-Mellin transform~\cite{Reddy1996,Zhang2019} and the bispectrum~\cite{Kakarala2009,Negrinho2013}. Alternatively, integral invariants~\cite{Manay2006,Feng2010} and moments can be computed. For the similarity group applied to images the original reference is \cite{Hu1962}, but see also~\cite{Hickman2011} for affine transformations, \cite{Flusser2009} for an implicit representation, and \cite{Papakostas2013} for their use in a binary pattern for image recognition.

The group that has been of particular interest for image analysis is the projective group, because of its ubiquity in camera models. Summarise these...
\cite{Suk2000,Suk2004,Hann2002a,Kogan2014}
\cite{Gros1992,Hubert2007}

Although there are computational challenges regarding the numerical approximation of derivatives on images, the fact that differential invariants are robust to occlusion, cheap to compute, and well-behaved with respect to small changes in the image, has made them popular for researchers in image analysis. 
Diff invs and sigs

An algorithm to compute differential and joint invariants and determine complete signature sets is described in \cite{Olver2005}. The entire set of invariants is computed using the method of moving frames (see Section~\ref{sec:movingframes}) and then the signature set of a maximal set of functionally independent invariants is identified. A third step is possible, in which the dimension of the signature set is reduced by eliminating those invariants whose values can be computed from the values of derivatives of some subset of the invariants.

\cite{Faugeras1994}
